---
title: "R Notebook"
output: html_notebook
---

# Packages and Data

```{r}
library(readr)
library(tidyr)
library(dplyr)
library(ggplot2)
theme_set(theme_bw())

options(stringsAsFactors=FALSE)
```


```{r}
library(rcrimeanalysis)
data(crimes)
crimes
```

```{r}
crimes_df <- data.frame(crimes)
head(crimes_df)
```

```{r}
table(crimes_df$primary_type) %>% 
        as.data.frame() %>% 
        arrange(desc(Freq))
```


```{r}
str(crimes_df)
```


```{r}
crimes_bar <- crimes_df %>% count(primary_type) %>% mutate(Percentage = round(n/nrow(crimes)*100,2)) %>% filter(rank(desc(Percentage)) <= 10)
ggplot(crimes_bar, aes(x = reorder(primary_type,-Percentage), y = Percentage)) +
  geom_bar(stat = "identity") +
  labs(title= "10 most common crimes by % of crimes citywide, Chicago ", x="Type of crime", y="Proportion of crimes reported citywide") +
  theme(axis.text.x=element_text(angle=45, hjust=1)) -> top10_crimes

top10_crimes
#ggsave("~/Downloads/top10_crimes.png", plot = top10_crimes)
```


$ primary_type        : chr  "WEAPONS VIOLATION" "THEFT" "OTHER OFFENSE" "BATTERY" ...
 $ description         : chr  "UNLAWFUL POSS OF HANDGUN" "$500 AND UNDER" "FALSE/STOLEN/ALTERED TRP" "SIMPLE" ...
 $ location_description: chr  "OTHER" "STREET" "STREET" "OTHER" ...
 $ arrest              : logi  TRUE FALSE TRUE TRUE FALSE FALSE ...
 $ domestic            : logi  FALSE FALSE FALSE FALSE FALSE FALSE ...
 $ beat                : num  832 1923 414 2031 235 ...
 $ district            : num  8 19 4 20 2 2 6 19 11 3 ...
 $ ward                : num  15 46 7 40 5 5 17 44 28 6 ...
 $ community_area      : num  66 6 46 4 41 41 71 6 26 69 ...
 $ fbi_code            : chr  "15" "6" "26" "08B" ...
 $ x_coordinate        : num  1161120 1170260 1192487 1156348 1187594 ...
 $ y_coordinate        : num  1858829 1924854 1853027 1932071 1868671 ...
 $ year                : num  2017 2019 2019 2017 2017 ...
 $ updated_on          : chr  "2/10/2018 15:50" "6/30/2019 15:56" "7/1/2019 16:17" "2/10/2018 15:50" ...
 $ latitude            : num  41.8 41.9 41.8 42 41.8 ...
 $ longitude           : num  -87.7 -87.6 -87.6 -87.7 -87.6 ...

```{r}
sel_col = c('arrest', 'latitude', 'longitude', 'year', 'fbi_code', 'domestic', 'district', 'ward')

crimes_input <- data.frame(crimes_df[sel_col], stringsAsFactors = F) #, 'year'

#factors
fac_col = sel_col[!sel_col %in% c('latitude', 'longitude', 'year')]

crimes_input[,fac_col] <- lapply(crimes_input[,fac_col], factor) 
```


```{r}
addNoAnswer <- function(x){
  if(is.factor(x)) return(factor(x, levels=c(levels(x), "Null")))
  return(x)
}

#Not for the arrest column

crimes_input[,fac_col[-1]] <- lapply(crimes_input[,fac_col[-1]], addNoAnswer) 
```



```{r}
#Lose two
crimes_input <- na.omit(crimes_input)

str(crimes_input)
```



## Models

```{r}
library(rpart)
library(rpart.plot)
crimes_tree <- rpart(arrest ~ ., data = crimes_input, method = 'class')
#crimes_tree
```


```{r}
predicted_arrest_dt <- predict(crimes_tree, crimes_input, type = 'class')
```

```{r}
prediction_table <- table(predicted_arrest_dt, crimes_input$arrest)
prediction_table 
```

```{r}
sum(predicted_arrest_dt == crimes_input$arrest) / nrow(crimes_input)
```


```{r}
library(nnet)

crimes_nn <- nnet(arrest ~ ., data = crimes_input, size = 10, maxit = 10000, trace = FALSE, MaxNWts = 5500)
```

```{r}
predicted_arrest_nn <- predict(crimes_nn, crimes_input[-1], type = 'class')
```


```{r}
prediction_table <- table(predicted_arrest_nn, crimes_input$arrest)
prediction_table 
```

```{r}
sum(predicted_arrest_nn == crimes_input$arrest) / nrow(crimes_input)
```


```{r}
library("randomForest")

crimes_rf <- randomForest(arrest ~ ., data = crimes_input, ntree=1000, keep.forest=FALSE,
                          importance=TRUE)

#varImpPlot(crimes_rf)
```



predicted_arrest_rf <- predict(crimes_rf, newdata = crimes_input[-1])
prediction_table <- table(predicted_arrest_rf, crimes_input$arrest)
prediction_table 
sum(predicted_arrest_rf == crimes_input$arrest) / nrow(crimes_input)


## Feature Importance

```{r}
# make dataframe from importance() output
feat_imp_df <- importance(crimes_rf) %>% 
    data.frame() %>% 
    mutate(feature = row.names(.)) 

# plot dataframe
ggplot(feat_imp_df, aes(x = reorder(feature, MeanDecreaseGini), 
                         y = MeanDecreaseGini)) +
    geom_bar(stat='identity') +
    coord_flip() +
    theme_classic() +
    labs(
      x     = "Feature",
      y     = "Importance",
      title = "Feature Importance: <Model>"
    )
```


## Decision Boundary

```{r}
x_min <- min(crimes_input$latitude) - 0.1
x_max <- max(crimes_input$latitude) + 0.1
y_min <- min(crimes_input$longitude) - 0.1
y_max <- max(crimes_input$longitude) + 0.1
hs <- 0.01
grid <- as.data.frame(expand.grid(seq(x_min, x_max, by = hs), seq(y_min, y_max, by =hs)))
names(grid) <- c('latitude','longitude')
```

```{r}
str(grid)
```


```{r}

grid$year <- 0
grid$fbi_code <- "Null"
grid$domestic <- "Null"
grid$district <- "Null"
grid$ward <- "Null"

str(grid)
```

```{r}
grid <- anti_join(grid, crimes_input, by=c('latitude', 'longitude'))
grid <- rbind(grid, crimes_input[-1])
str(grid)
```


```{r}
grid_predict <- predict(crimes_nn, newdata = grid, type = 'class')
```

```{r}
#theme_set(theme_bw())
p <- ggplot()+ geom_tile(aes(x = grid[,1],y = grid[,2],fill=as.character(grid_predict)), alpha = 0.5, show.legend = F) + 
  geom_point(data = crimes_input, aes(x=latitude, y=longitude, color = as.character(predicted_arrest_dt)), size = 2) +
  theme_bw(base_size = 15) +
  ggtitle('<Model> Boundary') +
  coord_fixed(ratio = 0.8) 
```


```{r}
p + scale_colour_grey(start = 0.6, end = 0.9) + theme_bw() + 
  theme(axis.ticks=element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        axis.text=element_blank(), axis.title=element_blank(), legend.position = 'none')  
```

## Rcrimeanalysis package

https://github.com/JSSpaulding/rcrimeanalysis

```{r}
nr_data <- head(crimes, n = 5000) #truncate dataset for near repeat analysis
out <- near_repeat_analysis(data = nr_data, tz = "America/Chicago", epsg = "32616")
path <- paste0("~/Downloads/series-png/") #path for iGraph networks out
name <- 1
# Save Image of Each igraph Network to Netpath Directory
library(igraph)
for(i in out){
    png(file = paste(path, "/series", name, ".png", sep = ""))
    plot(i, layout = layout_with_lgl, edge.color="orange",
    vertex.color = "orange", vertex.frame.color = "#ffffff",
    vertex.label.color = "black")
    dev.off()
    name <- name + 1
}
```

```{r}
int_out <- kde_int_comp(crimes, start1="1/1/2017", end1="3/1/2017",
                                start2="1/1/2018", end2="3/1/2018")
int_out
```

```{r}
library(leaflet) #needed to install basemap providers
library(leafsync) #creates plot of both maps
crime_sample <- head(crimes, n = 1000)
# Plot without Points
p1 <- crime_sample %>% kde_map(pts = FALSE)
# Plot with Incident Points
p2 <- crime_sample %>% kde_map()
leafsync::sync(p1,p2)
```

```{r}
library(prophet)
ts_forecast(crimes, start = c(2017, 1, 1))
```

```{r}

```

